The core transcriptome of the mammal placenta

### 2016-08-12 manuscript/manuscript.Rnw
add keywords
switch to colwidth

<<load.libraries,echo=FALSE,results="hide",warning=FALSE,message=FALSE,error=FALSE,cache=FALSE>>=
opts_chunk$set(dev="cairo_pdf",out.width="\\textwidth",out.height="0.7\\textheight",out.extra="keepaspectratio")
opts_chunk$set(cache=TRUE, autodep=TRUE)
options(device = function(file, width = 8, height = 7, ...) {
  cairo_pdf(tempfile(), width = width, height = height, ...)
})
options(scipen = -2, digits = 0)
library("data.table")
library("ggplot2")
library("reshape2")
library("xtable")
library("grid")
library("gridExtra")
library("ape")
library("ggtree")
library("topGO")
library("org.Hs.eg.db")
library("scales")
library("magrittr")
library("tidyr")

@@

\textbf{Keywords:} mammal, gene expression, evolution, RNA-seq, placenta

\end{abstract}
\end{abstractbox}
\end{frontmatter}

>>>>

<<load.libraries,echo=FALSE,results="hide",warning=FALSE,message=FALSE,error=FALSE,cache=FALSE>>=
opts_chunk$set(dev="cairo_pdf",out.width="\\colwidth",out.height="0.7\\textheight",out.extra="keepaspectratio")
opts_chunk$set(cache=TRUE, autodep=TRUE)
options(device = function(file, width = 8, height = 7, ...) {
  cairo_pdf(tempfile(), width = width, height = height, ...)
})
options(scipen = -2, digits = 0)
library("data.table")
library("ggplot2")
library("reshape2")
library("xtable")
library("grid")
library("gridExtra")
library("ape")
library("ggtree")
library("topGO")
library("org.Hs.eg.db")
library("scales")
library("magrittr")
library("tidyr")

@@

\end{abstract}

\begin{keyword}
mammal \sep  gene expression \sep evolution \sep RNA-seq \sep placenta
\end{keyword}

\maketitle
